Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-08 paper/paper.tex
[paper] updated results section

\end{abstract}
Recent years have witnessed advances in the  development of Big Data frameworks like Apache Spark and Apache Flink. For instance, both frameworks support real-time data 
stream processing. The question of which platform is superior to the other still open. 
In this report, we provide a performance comparison of streaming data processing in Apache Spark and Apache Flink by measuring different performance metrics (latency and throughput). In addition, we cover some key aspects of streaming data applications and how they are handled in the two frameworks. The experiment is done using multiple streaming workloads over real-world datasets.
\section{Introduction}

@@

Figure 5 shows the results of latency measurements of the streaming workloads in Spark and Flink. The observed values present the mean value of multiple trails and measurements. Measurements for different batch intervals are given in Spark Streaming,  if we decrease  will not get better latency but it is even getting  worse. Results show that Flink outperform Spark streaming in term of processing latency in the both evaluation workloads.

@@

\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{latency1.png}
\caption{Latency of Sector Change Detection }

@@

@@

In this report, we present an experimental evaluation of the streaming processing performance and capabilities of Apache Spark and Apache Flink. We carried our experiment over aircraft potions provided in the context of EU Datacorn  project, we developed two streaming workloads to cover general aspects of real-time stream processing tasks, and we measured the latency and throughput of those workloads within the solution of Spark and Flink. Results show that Flink outperforms Spark Streaming in term of processing latency. Furthermore, Flink's processing model is well-suited to  the stream processing tasks, there is no need to manage the Stream's state and batch interval as it is in Spark streaming. Additionally, Flink operates over the individual record of the data stream, not like Spark Streaming that processes the input data stream as micro-batches. In Summary, Flink is true stream processing framework.

In future work, we plan to carry our experiments over cluster of computers not just only on single computer. In addition, we will cover more aspects of streaming processing and developing more evaluation workloads.

>>>>

\end{abstract}
Recent years have witnessed advances in the  development of Big Data frameworks like Apache Spark and Apache Flink. For instance, both frameworks support real-time data 
stream processing. The question of which platform is superior to the other still open. 
In this report, we provide a performance comparison of streaming data processing in Apache Spark and Apache Flink by measuring different performance metrics (latency and throughput). In addition, we cover some key aspects of streaming data applications and how they are handled in the two frameworks. The experiment is done using multiple streaming workloads over real-world datasets. Results show that Flink outperform Spark streaming in term of latency.  
\section{Introduction}

@@

Figure 5 shows the results of the latency measurements of the streaming workloads in Spark and Flink. The observed values present the mean value of multiple trails and measurements. Measurements for different batch intervals are given in Spark Streaming, we noticed that making the batch time too small does not give best latency results. Results show that Flink outperform Spark streaming in term of processing latency in the two evaluation workloads.

@@

\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{latency2.png}
\caption{Latency of Sector Change Detection }

@@

The  measurements of throughput for the two streaming workloads are give in Figure 6. The observed values reflect the mean of throughput (message/minute) 
 in Spark streaming and Flink for multiple executions. Also for Spark streaming we tested different 
 batch times. Results show that

\begin{figure}[h]
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{latency1.png}
  \caption{Throughput of Statistics Computation}

\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{latency1.png}
\caption{Throughput of Sector Change Detection }

\end{subfigure}
\caption{Throughput Measurements}
\label{fig:fig}
\end{figure}

\newpage

@@

In this report, we present an experimental evaluation of the stream processing performance and capabilities of Apache Spark and Apache Flink. We carried our experiment over aircraft positions datasets provided by the Datacorn project, we developed two streaming workloads to cover general aspects of real-time stream processing tasks. Additionally, and we measured the latency and throughput of those workloads solution of Spark and Flink. Results show that Flink outperforms Spark Streaming in term of processing latency. Furthermore, Flink's processing model is well-suited to the stream processing tasks, there is no need to manage the Stream's state and batch interval as it is in Spark streaming. Moreover, Flink operates over the individual record of the data stream, while Spark Streaming  processes the input data stream as micro-batches. In Summary, Flink is true stream processing framework. On the other hand, we noticed that finding online resources related to Spark is easier than to Flink.

In future work, we plan to carry our experiments over cluster of computers not just only on single computer. In addition, we will cover more aspects of real-time data stream processing and developing more evaluation workloads.
